CTest Integration of Sikuli Automated GUI Testing

### 2011-06-08 Documentation/Article.tex
starts editing paper
authors
updated article

% The title should be descriptive enough for people to be able to find
% the relevant document. 
\title{}

@@

% At minimum, give your name and an email address.  You can include a
% snail-mail address if you like.
\author{}
\authoraddress{ Harvard Medical School, Megason lab}

@@

\tableofcontents

\section{Introduction}
\section{Sikuli}
\section{Integration with CTest}
\section{Example}
\section{Conclusion}

>>>>

% The title should be descriptive enough for people to be able to find
% the relevant document.
\title{CTest Integration of Sikuli Automated GUI Testing}

@@

% At minimum, give your name and an email address.  You can include a
% snail-mail address if you like.
\author{Evan Schwab, Lydie Souhait, Nicolas Rannou, Kishore Mosaliganti\\
Arnaud Gelas, Sean Megason}
\authoraddress{Harvard Medical School, Megason lab}

@@

\tableofcontents
% ------------------------------------------------------------------------
\section{Introduction}

% ------------------------------------------------------------------------
\section{Sikuli}

% Feel free to change section titles
\subsection{What is sikuli?}
Sikuli is a programming language that uses screen shot images as variables
and objects in order to automate graphical user interface functions. The
Sikuli program is comprised of an IDE where the user can write scripts that 
include screen shot thumbnails so they can visually track the functions of
their code. The Sikuli Script is built on a Jython (Python for Java platform)
library which uses Python syntax in addition to a number of special Sikuli
functions for aquiring and handling screenshot images and performing mouse,
keyboard actions, the most useful of which are conveniently found as buttons
on the Sikuli IDE.

One of Sikuli's primary uses is the automation of GUI testing for software
developers.

\subsection{Simple of example} % not related to gofigure...

\begin{figure}[htp]
 \centering

 \caption{here is my caption}
 \label{fig:SimpleExample}
\end{figure}

% ------------------------------------------------------------------------
\section{Integration with CTest}
% I'll write it this part

% ------------------------------------------------------------------------
\section{Example}

% ------------------------------------------------------------------------
\section{Conclusion}
